\documentclass[letterpaper,11pt]{article}
    
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{soul}  
\usepackage{xcolor} 
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
    

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
    
% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}
    
\urlstyle{same}
    
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
    
% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
    
% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1
    
%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
    
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
    
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}
    
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
    
    
%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
    
\begin{document}
\small
%----------HEADING----------
\begin{center}
    \vspace{-6pt}
    \textbf{\Huge \scshape Pankaj Kumar} \\ \vspace{6pt}
    \small 
    \faIcon{envelope}
    \textbf{\href{mailto:kumarpankaj3404@gmail.com}
    {\textcolor{blue}{\underline{kumarpankaj3404@gmail.com}}}}  $  $
    \faIcon{linkedin}
    \href{https://www.linkedin.com/in/pankaj-kumar-513a10298}{\textcolor{blue}{\underline{\textbf{Linkedin}}}}  $  $ 
    \faIcon{github}
    \href{https://github.com/kumarpankaj3404}{\textcolor{blue}{\underline{\textbf{GitHub}}}}  $  $
    \faIcon{phone}
    {\textcolor{blue}{\underline{\textbf{+91-8638217797}}}}  $  $

    \vspace{6pt}

    \faIcon{globe}
    \href{https://pankajkumar.app}{\textcolor{blue}{\underline{\textbf{pankajkumar.app}}}} $  $
\end{center}

\vspace{-15pt}
    
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Lovely Professional University}{Aug 2023 -- Present}
      {Bachelor of Technology in Computer Science and Engineering}{CGPA: 8.19}
    \resumeSubheading
      {Kendriya Vidyalaya, Hakimpet, Secunderabad}{Apr 2021 -- Mar 2023}
      {Intermediate}{Percentage: 87.4\%}
    \resumeSubheading
      {Kendriya Vidyalaya, Hakimpet, Secunderabad}{Apr 2020 -- Mar 2021}
      {Matriculation}{Percentage: 71.2\%}
  \resumeSubHeadingListEnd
    
%-----------TRAINING-----------
\section{Training}
\resumeSubHeadingListStart
  \resumeSubheading
    {Cipher School}{Jun 2025 -- Jul 2025}
    {Cloud Computing AWS}{}
    \resumeItemListStart
      \resumeItem{Completed an industry-aligned AWS Cloud Computing training focused on EC2, VPC, Load Balancing, Auto Scaling, IAM, S3 and CI/CD with hands-on deployment practices.}
      \resumeItem{Developed and deployed a multi-instance web application architecture on AWS using EC2, ALB, security groups, and networking concepts.}
      \resumeItem{Gained practical skills in cloud deployment, instance management, monitoring, automation, and optimizing cloud workloads following AWS best practices.}
    \resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
\vspace{-5pt}
\resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Restaurant Order Management} $|$ \footnotesize\emph{{Node.js, Express.js, MongoDB, Redux, React.js, Tailwind}}}
      {\href{https://github.com/kumarpankaj3404/Resturant-Frontend}{\faGithub\ \textcolor{blue}{\textbf{GitHub}}}}
      \resumeItemListStart
      \vspace{2pt}
        \resumeItem{Built a modular MERN-based ordering system with JWT auth and complete menu/order CRUD, improving API performance by 35\% through optimized routing and MongoDB indexing.}
        \resumeItem{Developed a responsive frontend using React.js, Redux Toolkit, Tailwind, and Motion, reducing state-related re-renders by 30\% and delivering smoother UI interactions.}
        \resumeItem{Engineered structured business logic, reusable validation middleware, and centralized error handling to standardize API responses, reduce runtime failures, and enhance system reliability.}
      \resumeItemListEnd
    \vspace{-10pt}

    \resumeProjectHeading
      {\textbf{\href{https://unimart.pankajkumar.app/}{\textcolor{blue}{\underline{Unimart - Real-Time Delivery Tracking}}}} $|$ \footnotesize\emph{{Node.js, Express.js, MongoDB, Socket.IO, React.js, Redux}}}
      {\href{https://github.com/kumarpankaj3404/Unimart-Frontend}{\faGithub\ \textcolor{blue}{\textbf{GitHub}}}}
      \resumeItemListStart
      \vspace{2pt}
        \resumeItem{Built a production-ready full-stack delivery platform with role-based authentication for Customers, Delivery Partners, and Admins using JWT, Express.js, and MongoDB with clean, modular API architecture.}
        \resumeItem{Implemented real-time order tracking using Socket.IO and WebSockets, streaming live driver GPS locations to customers on interactive maps (React Leaflet) for an Uber-like delivery experience.}
        \resumeItem{Integrated real-time client-side communication and mapping workflows using Socket.IO Client and React Leaflet delivering sub-500ms live location updates, supporting 100+ concurrent active orders, and improving delivery visibility and user trust.}
      \resumeItemListEnd
    \vspace{-10pt}

    \resumeProjectHeading
      {\textbf{\href{https://recipe-finder-pankaj.vercel.app/}{\textcolor{blue}{\underline{Recipe Finder}}}} $|$ \footnotesize\emph{{React.js, Redux, Tailwind CSS, Supabase}}}
      {\href{https://github.com/kumarpankaj3404/recipe-finder}{\faGithub\ \textcolor{blue}{\textbf{GitHub}}}}
      \resumeItemListStart
      \vspace{2pt}
        \resumeItem{Engineered a Full-stack recipe platform using React and Supabase, achieving 100\% data persistence for user-specific favorite lists through secure backend integration.}
        \resumeItem{Architected centralized state management using Redux Toolkit, reducing prop-drilling by 80\% and ensuring seamless data flow across search and category filters.}
        \resumeItem{Optimized UI performance with Tailwind CSS and React Router, delivering a fully responsive experience with sub-1 second page transitions across all devices.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

\vspace{-15pt}
    
%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
        \textbf{Languages:} Java, JavaScript, TypeScript, C, C++ \\
        \textbf{Frontend:} HTML, CSS, Tailwind CSS, React.js, Next.js, Redux Toolkit \\
        \textbf{Backend:} Node.js, Express.js, REST APIs, MongoDB, JWT, Cloudinary \\
        \textbf{Tools/Platforms:} GitHub, Git, Netlify, Render, Postman, Google Search Console \\
        \textbf{Soft Skills:} Problem-Solving, Project Management, Time Management \\
    }}
\end{itemize}
    
\vspace{-15pt}
    
%-----------CERTIFICATIONS & ACHIEVEMENTS---------------
\section{Certifications \& Achievements}
\resumeSubHeadingListStart
    \resumeItemListStart
        \resumeItem{\textbf{Certifications:} Node.js by Scaler (Feb 2026), Social Networks by NPTEL (Oct 2025), MERN Stack by Udemy (Dec 2024), Responsive Web Design (Nov 2023).}
        \resumeItem{\textbf{Leetcode Achievements:} Solved 150+ Data Structures and Algorithms problems, covering Arrays, Strings, Linked Lists, Trees, Graphs, Recursion, and Dynamic Programming.}
        \resumeItem{\textbf{HackerRank Badges:} Earned a Gold Level Badge in Java on HackerRank by solving complex algorithmic challenges and accumulating over 300+ points.}
    \resumeItemListEnd
\resumeSubHeadingListEnd
    
\end{document}